---
title: 'Developing Data Products: Final Project'
author: "George"
date: "December 23, 2016"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
```

## Instructions

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

## Data: Daily sales by product

```{r mydata, echo = TRUE}
sales_df <- data.frame(product1=sample(8000:10000,365,rep=TRUE),
                 product2=sample(4000:5000,365,rep=TRUE), 
                 product3=sample(15000:20000,365,rep=TRUE)) 
sales_df$dayofyear<-seq.int(nrow(sales_df))
head(sales_df)
```

## Plot: Daily sales by product

```{r time series chart, echo= FALSE}
f <- list(
  family = "Courier New, monospace",
  size = 18,
  color = "#7f7f7f"
)
x <- list(
  title = "day of the year",
  titlefont = f
)
y <- list(
  title = "sales (volume)",
  titlefont = f
)
p <- plot_ly(sales_df, x = ~dayofyear, y = ~product1, name = 'product 1', type = 'scatter', mode = 'lines')%>%
  add_trace(y = ~product2, name = 'product 2', mode = 'lines') %>%
  add_trace(y = ~product3, name = 'product 3', mode = 'lines')%>%
  layout(xaxis = x, yaxis = y)
p
```

## Code

```{r code, echo= TRUE}
f <- list(
  family = "Courier New, monospace",
  size = 18,
  color = "#7f7f7f"
)
x <- list(
  title = "day of the year",
  titlefont = f
)
y <- list(
  title = "sales (volume)",
  titlefont = f
)
p <- plot_ly(sales_df, x = ~dayofyear, y = ~product1, name = 'product 1', type = 'scatter', mode = 'lines')%>%
  add_trace(y = ~product2, name = 'product 2', mode = 'lines') %>%
  add_trace(y = ~product3, name = 'product 3', mode = 'lines')%>%
  layout(xaxis = x, yaxis = y)
p
```