World airports Map
========================================================
author: George Theologou
date: "December 23, 2016"
output: ioslides_presentation

What is this application?
========================================================
This application is for locating airports and identifying how many airlines fly from each airport. Two data sets were downloaded from OpenFlights.org. 

**1. Route database**

The route database contains 59036 routes between 3209 airports on 5.

**2. Airport database**

The airport database contains 6977 airports spanning the globe, as shown in the map above.

These two files were then joined to create the dataset used for this App.

Data sets link: http://openflights.org/data.html
Note: The current data might not be 100% accurate.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r}
library(webshot)
library(leaflet)
library(tidyverse)

df <- read_csv("../data/processed/airlinesbyairport.csv")  
print (df)
min = 1
max = 900
filtered_df <- df%>%filter(count >= min & count <= max)
filtered_df <- filtered_df%>%select(latitude,longitude)

greenLeafIcon <- makeIcon(
  iconUrl = "http://seeklogo.com/images/D/departure-flights-airport-sign-logo-A9A341DA0F-seeklogo.com.gif",
  iconWidth = 22, iconHeight = 22,
  iconAnchorX = 22, iconAnchorY = 22
  )

airportnames <- df%>%mutate(labels=paste(airportname))%>%select(labels)
airlines <- df%>%mutate(labels=paste(count))%>%select(labels)

leaflet() %>%
addProviderTiles( "OpenStreetMap.HOT",options = providerTileOptions(noWrap = TRUE)) %>%
addMarkers(data = filtered_df, clusterOptions = markerClusterOptions(), icon = greenLeafIcon,popup = paste("<strong>Airport name: </strong>","<br>",as.character(airportnames$labels),"<br>","<hr>", "<em>Airlines flying: </em>","<br>","<em>",as.character(airlines$labels),"</em>")
)


```


## Slide with Plot

```{r pressure}
plot(pressure)
```

