---
title: "World airports Map"
author: "George"
date: "December 25, 2016"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
```

## What is this application?

This application is for locating airports and identifying how many airlines fly from each airport. Two data sets were downloaded from OpenFlights.org. 

**1. Route database**

The route database contains 59036 routes between 3209 airports on 5.

**2. Airport database**

The airport database contains 6977 airports spanning the globe, as shown in the map above.

These two files were then joined to create the dataset used for this App.

Data sets link: http://openflights.org/data.html

Note: The current data might not be 100% accurate.

## World airports Map

```{r, echo=FALSE, message=FALSE}
library(webshot)
library(leaflet)
library(tidyverse)

df <- read_csv("../data/processed/airlinesbyairport.csv")  
min = 1
max = 900
filtered_df <- df%>%filter(count >= min & count <= max)
filtered_df <- filtered_df%>%select(latitude,longitude)

greenLeafIcon <- makeIcon(
  iconUrl = "http://seeklogo.com/images/D/departure-flights-airport-sign-logo-A9A341DA0F-seeklogo.com.gif",
  iconWidth = 22, iconHeight = 22,
  iconAnchorX = 22, iconAnchorY = 22
  )

airportnames <- df%>%mutate(labels=paste(airportname))%>%select(labels)
airlines <- df%>%mutate(labels=paste(count))%>%select(labels)
```

```{r, echo=TRUE}
leaflet() %>%
addProviderTiles( "OpenStreetMap.HOT",options = providerTileOptions(noWrap = TRUE)) %>%
addMarkers(data = filtered_df, clusterOptions = markerClusterOptions(), icon = greenLeafIcon,
           popup = paste("<strong>Airport name: </strong>","<br>",as.character(airportnames$labels),"<br>","<hr>", 
                         "<em>Airlines flying: </em>","<br>","<em>",
                         as.character(airlines$labels),"</em>")
)
```

## Functionality

- Navigate through the map, zoom in/out and click on clusters of airports
- Get the number of airlines on a selected airports
- Filter on airports with a range of volume of airlines

## Appendix

Shiny app: https://georgeaueb.shinyapps.io/reactive_map/

Github Repo: https://github.com/GeorgeTheologou/dataproductproject

Rpub presentation: http://rpubs.com/georgeaueb/237473

